---
title: "homework5"
author: "wz2631"
date: "2022-11-16"
output: github_document
---

```{r, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	fig.height = 8,
	fig.width = 10,
	echo = TRUE,
	warning = FALSE,
	out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, the dataframe that includes the list of all files in that directory and the complete path to each file was created. Next, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2
#### Import and describe the raw data.
The code chunk below imports and cleans the data in `homicide-data.csv`. 
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names()
```
There are `r ncol(homicide_df)` columns and `r nrow(homicide_df)` rows in this dataframe, and the important variables included are `r colnames(homicide_df)`, which are used to describe the information of homicides in 50 large U.S. cities.

#### Create a city_state variable by mutate function.
```{r}
homicide_df =
  homicide_df %>% 
  mutate(city_state = str_c(city, ', ',state))
```

#### Summarize within cities to obtain the total number of homicides.
```{r}
homicide_total = homicide_df %>% 
  group_by(city_state) %>% 
  count(city_state) %>% 
  summarize(n) 
homicide_total %>% 
  knitr::kable()
```

####  Summarize within cities to obtain the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
```{r}
homicide_unsolved = homicide_df %>% 
  mutate(
    homicide_statu =  ifelse(disposition != "Closed by arrest", "unsolved", "solved")) %>%
  group_by(city_state) %>% 
  summarize(
    n_unsolved = sum(homicide_statu == "unsolved")) 
homicide_unsolved %>% 
  knitr::kable()
```

####